Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-28 paper/authors.tex
update authors
merge fpscenarios plot to paper

%PENDING
\author[0000-0003-2989-7774]{C. Bergmann}
\affilation{Exoplanetary Science at UNSW, School of Physics, UNSW
Sydney, NSW 2052, Australia}

@@

%
% SG4 contributors
%
\author[0000-0002-0619-7639]{C.~Ziegler}
\affiliation{Dunlap Institute for Astronomy and Astrophysics,
University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4,
Canada}

>>>>

%PENDING
\author[0000-0003-2989-7774]{C. Bergmann}
\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
Sydney, NSW 2052, Australia}

@@

%
% SG4 contributors
%
\author[0000-0002-0619-7639]{C.~Ziegler} % carl.ziegler@dunlap.utoronto.ca
\affiliation{Dunlap Institute for Astronomy and Astrophysics,
University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4,
Canada}

%FIXME ORCIDs
\author{C.~Brice\~{n}o} % cbriceno@ctio.noao.edu
\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La
Serena, Chile}

\author{N.~Law} % nlaw@unc.edu
\affiliation{Department of Physics and Astronomy, The University of
North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}

\author{A.~W.~Mann} % awmann@unc.edu
\affiliation{Department of Physics and Astronomy, The University of
North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}

### 2020-05-28 paper/ms.tex
merge fpscenarios plot to paper

@@

\tn\ has been reported as a member of \cn\ by multiple independent 
investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
%FIXME FIXME finish these citations

@@

\subsubsection{Literature Membership}
The membership of \tn\ in \cn\ was noted by \citet{oh_comoving_2017},
in what they dubbed ``Group 5''.
Analyzing the clusters of \citet{oh_comoving_2017},
\citet{bochanski_fundamental_2018} fitted the Gaia, 2MASS, and
WISE photometry with MIST isochrones, and reported stellar masses,
radii, metallicities, ages, distances, and extinction for 9754 stars,
including \tn.

\tn\ was also listed as a member of ``Theia 92'' by
\citet{kounkel_untangling_2019}.
These authors identified 999 candidate cluster members, and
reported a cluster isochrone age $\log t = 7.55$ with uncertainty
$\approx 0.15\,{\rm dex}$.

@@

@@

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

>>>>

"""Although IC 2602 does not belong to Sco OB2, it is
spatially and dynamically a close relative, and for this reason
we include it in this work, if even marginally"" (Damiani+2019).
"""We also find that the open cluster IC 2602 has a similar dynamics
to Sco OB2, and its PMS members are currently evaporating and forming
a diffuse (size 10deg) halo around its double-peaked core"""

@@

\tn\ has been reported as a member of \cn\ by multiple independent 
investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
%FIXME FIXME finish these citations
%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed as
%IC2602

@@

\subsubsection{Literature Membership}
The membership of \tn\ in \cn\ was noted by \citet{oh_comoving_2017},
in what they dubbed ``Group 5''.
Analyzing the clusters of \citet{oh_comoving_2017},
\citet{bochanski_fundamental_2018} fitted the Gaia, 2MASS, and
WISE photometry with MIST isochrones, and reported stellar masses,
radii, metallicities, ages, distances, and extinction for 9754 stars,
including \tn.
%Bochanski reported:
%logAge 9.38 +0.42 -0.26
%dist 138.3 +7.0 -7.2
%A_v = 0.27 +0.18 - 0.18
%

\tn\ was also listed as a member of ``Theia 92'' by
\citet{kounkel_untangling_2019}.
These authors identified 999 candidate cluster members, and
reported a cluster isochrone age $\log t = 7.55$ with uncertainty
$\approx 0.15\,{\rm dex}$.
They reported an average extinction of Av=0.243 mag.

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
    {\it Bottom}: for unassociated companions along the same line of
    sight.
		\label{fig:rawzoom}
	}
\end{figure*}

@@

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
% This research has made use of the SVO Filter Profile Service
% (\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
% MINECO through grant AYA2017-84089
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%
